The LHC as a Neutrino-Ion Collider

### 2023-12-05 referee/referee-reply.tex

	Following the referee's suggestion, the results which only include the statistical errors
	are now labelled "FPF$\star$" while the one that also account for the systematics are labelled "FPF".
        %
        We have also extended the rationale for showing results in the statistics-only scenario, alongside the
        considerations described above.

	\item {\it Section 4 and elsewhere. Given these are HL-LHC projections, somewhere these should
		be compared with the HL-LHC PDFs of Ref [34]. This would surely be the fairer
		comparison, or in any case will give a clearer picture of where things may stand.
	}

	The reason why we did not provide comparisons with the HL-LHC PDFs of Ref. [34] is because
	the pseudodata used to determine these PDFs were produced with the PDF4LHC15 set which
	does not account for the recent LHC measurements. The most consistent comparisons would
	be to re-do the analysis done in ref. [34] using PDF4LHC21 and then compare the resulting PDFs 
	with our determination, something which is clearly outside the scope of this paper.

        This said, to answer the question from the referee, we have repeated the phenomenological study of Sect 4
        comparing PDF4LHC15 with PDF4LHC15+HLHC PDFs for the same processes.
        %
        Specifically, we have added to the paper an Appendix where the phenomenology study of Sect 4 is repeated
        now for the PDF4LHC15 with PDF4LHC15+HLHC PDFs.

        This comparison highlights the complementarity between the two experiments
in terms of PDF constraints, being fully orthogonal and arising from different
scattering process.
%
Furthermore, the FPF constraints benefit from the valuable property
that an eventual contamination from new physics on the PDF fits 
can be neglected, since this process is driven by $Q^2$ values outside 
the possible presence of BSM physics, at least concerning new heavy states.
%
Therefore, the ultimate sensitivity on high-precision observables being
obtained by integrating the constraints both from the HL-LHC and from the FPF
in the same global determination of PDFs.

@@

\item{\it p.9 l. 41-43 col.2 “We note that … in our estimation.” (see also the conclusions p. 27 l. 52-55 col.1) I am puzzled by this statement. It is well known that flux systematics in Faser and SND@CERN play a prominent role and set the normalization (and shape?) of eqn 2.12. How can you ignore such an important effect in your analyses? Even if the PDF constraints are marginally affected by the normalization of the neutrino flux, some of your considerations about the on-axis (faser and faser2) versus the off-axis experiments (SND@CERN and its upgrades) may be affected by flux uncertainties. Can you comment on it in the paper?}

  Indeed, the large neutrino flux uncertainties are well established, and the shape and normalization of the flux can vary widely between different models, although the neutrino muon component which is mostly relevant for neutrino DIS experiments is the one which is known the best.

  It is important to note that neutrino measurements actually constrain the product of flux and cross-section - each of these components brings an uncertainty with it, and a full analysis with real data would constrain them simultaneously. We wish to motivate this joint analysis by calculating the  impact that FPF data can bring to a PDF fit. In this sense, by taking the flux to be known we can understand the full reach of FPF data on cross-section measurements, analogous to what was done in 2309.10417. Moreover, projections of FPF data on flux measurements has shown that HL-LHC data can bring flux uncertainties to a sub-percent level.

  We would like to raise two more considerations which justify, in this work, to assume that the incoming neutrino
  fluxes are known:
  \begin{itemize}
  \item As shown in appendix A in the original version of the paper (now moved to Sect 3), FASER$\nu$ and SND@LHC data from run III do not have sensitivity on the modelling of the neutrino-nucleus interaction cross-section.
    %
    This means that these measurements can be safely used, before the start of the FPF, to cross-calibrate
    incoming neutrino fluxes and markedly improve their predictions for subsequent analysis.
    %
    Just due to this, by the time the FPF starts data taking the neutrino fluxes will be known
    more precisely than now.

### 2023-12-05 journal_sub/app-hllhc.tex
done revision

Here we revisit the phenomenology studies as in
Sec.~\ref{sec:pheno} but using the High-Luminosity LHC (HL-LHC) PDF 
from~\cite{AbdulKhalek:2018rok}.
%
Such comparisons present a complementary study to the impact seen both at the PDF 
and prediction level shown in Sec.~\ref{sec:pheno}. The PDF constraints from the 
FPF and HL-LHC experiments are fully orthogonal in that the former have the very 
important property that possible contamination from new physics on the PDF fits 
can be completely ignored, since this process is driven by $Q^2$ values outside 
the possible presence of BSM physics.
%
Specially, should anomalies be revealed at the HL-LHC, having the fully independent
validation of the large-$x$ PDFs provided by the FPF would be extremely valuable 
for its interpretation.

In Fig.~\ref{fig:HLLHC_pheno_integrated} The same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
now comparing the PDF4LHC15 baseline predictions with those based
on the PDFs including HL-LHC pseudo-data from~\cite{AbdulKhalek:2018rok}.
%
Specifically, we consider the HL-LHC PDF projections
from ``Scenario B'', corresponding to an intermediate scenario for the expected reduction
of systematic uncertainties.
 %
Concerning the fiducial cross-sections, a significant reduction in PDF uncertainties
is seen, reaching up to a factor of four for processes involving single boson productions. 
Such a significant decrease in the PDF uncertainties is also observed at the differential
level.

>>>>

Here we revisit the phenomenology studies of
Sect.~\ref{sec:pheno} using the HL-LHC PDF impact projections
presented in~\cite{AbdulKhalek:2018rok}.
%
These projections were obtained with the same Hessian profiling strategy
as discussed in Sect.~\ref{sec:dis_pseudodata}, with the important
difference that the prior PDF set was PDf4LHC15 rather than
PDF4LHC21.
%
Therefore, while a direct comparison with the results presented in
Sect.~\ref{sec:pheno} is not possible due to the use of a different prior,
we can assess the relative reduction of PDF uncertainties in both cases,
and hence compare the reach on the PDFs of the FPF neutrino structure functions
and that of the HL-LHC measurements considered in the analysis of~\cite{AbdulKhalek:2018rok}.

This comparison of the relative PDF sensitivity of the FPF and
the HL-LHC data is interesting given that the  constraints from the 
two experiments are fully orthogonal and arise from completely different
scattering process.
%
Furthermore, the FPF constraints benefit from the valuable property
that an eventual contamination from new physics on the PDF fits 
can be neglected, since this process is driven by $Q^2$ values outside 
the possible presence of BSM physics (at least concerning new heavy particles).
%
Specially, should anomalies be revealed at the HL-LHC, having the independent
validation of the large-$x$ PDFs provided by the FPF would be extremely valuable 
for its interpretation.

Fig.~\ref{fig:HLLHC_pheno_integrated} displays the
same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
now comparing the PDF4LHC15 baseline predictions with those based
on the PDFs including HL-LHC pseudo-data from~\cite{AbdulKhalek:2018rok}.
%
Specifically, we consider the HL-LHC PDF projections
from ``Scenario B'', corresponding to an intermediate scenario for the expected reduction
of systematic uncertainties.
%
In general, the relative reduction on PDF uncertainties provided by the HL-LHC experiments
is more marked as in the case of the FPF pseudo-data, with the important caveat that
PDF4LHC21 already includes much more LHC data in comparison with its predecessor,
PDF4LHC15.
%
Another possible limiting assumption used in~\cite{AbdulKhalek:2018rok} is that
correlated uncertainties can be reliable estimated at the few-permille level
relevant for the intepretation of the HL-LHC data, something that is proving quite challenging
even for Run I and II measurements.

Nevertheless, the message obtained by comparing Fig.~\ref{fig:HLLHC_pheno_integrated} 
 with Fig.~\ref{fig:NNPDF40_pheno_integrated} is that of complementarity,
with the ultimate sensitivity on high-precision observables being
obtained by integrating the constraints both from the HL-LHC and from the FPF
in the same global determination of PDFs.

### 2023-12-05 journal_sub/sec-introduction.tex
done revision

The outline of this paper is as follows.
%
Sect.~\ref{sec:dis_pseudodata} describes the procedure
adopted to generate projections for neutrino DIS structure functions at the LHC
and the methodology used to include these into PDF fits.
%
The impact of such LHC structure function measurements on proton and nuclear
PDFs is quantified in Sect.~\ref{sec:protonPDFs}, with the
associated implications for precision phenomenology
at the HL-LHC assessed in Sect.~\ref{sec:pheno}.
%
We summarise in Sect.~\ref{sec:summary}, where we also consider possible
directions for follow-up research.
%
Additional results are collected in two appendices:
App.~\ref{app:fasernu_runIII_impact} studies the constraints provided by
FASER$\nu$ measurements at Run III, and App.~\ref{app:nPDF_impact_appendix}
quantifies the stability of the nPDF impact projections with respect
to input variations.

>>>>

The outline of this paper is as follows.
%
Sect.~\ref{sec:dis_pseudodata} describes the procedure
adopted to generate projections for neutrino DIS structure functions at the LHC
and the methodology used to include these into PDF fits.
%
The impact of such LHC structure function measurements on proton and nuclear
PDFs is quantified in Sect.~\ref{sec:protonPDFs}, with the
associated implications for precision phenomenology
at the HL-LHC assessed in Sect.~\ref{sec:pheno}.
%
We summarise in Sect.~\ref{sec:summary}, where we also consider possible
directions for follow-up research.
%
Additional results are collected in two appendices:
App.~\ref{app:comparisons_with_HLLHC} revisits
the phenomenological studies of
Sect.~\ref{sec:pheno} using the HL-LHC PDF impact projections
presented in~\cite{AbdulKhalek:2018rok}, while App.~\ref{app:nPDF_impact_appendix}
quantifies the stability of the nPDF impact projections with respect
to input variations.

### 2023-12-05 journal_sub/sec-pheno.tex
done revision

>>>>

For completeness, App.~\ref{app:comparisons_with_HLLHC} revisits
the phenomenological studies  presented in this section for the fiducial cross-sections
in terms of the  HL-LHC PDF impact projections of~\cite{AbdulKhalek:2018rok}.
%
This comparison highlights the complementarity between the two experiments
in terms of PDF constraints, being fully orthogonal and arising from different
scattering process.
%
Furthermore, the FPF constraints benefit from the valuable property
that an eventual contamination from new physics on the PDF fits 
can be neglected, since this process is driven by $Q^2$ values outside 
the possible presence of BSM physics, at least concerning new heavy states.
%
Therefore, the ultimate sensitivity on high-precision observables being
obtained by integrating the constraints both from the HL-LHC and from the FPF
in the same global determination of PDFs.
